On exponential sums arising from the classical doubling method

### 2025-03-24 paper.tex
Comment
Calvin changes

\subsection{TODO list}
\begin{enumerate}
	\item In the computations of $\dblGammaFactor{\pi}{\chi}{\fieldCharacter}$ in terms of Deligne--Lusztig we should say that when we take a torus of $\GroupExtension{G}$ and intersect it with $G$ we get a torus of $G$ and hence it suffices to compute whatever we are computing.
	\item The proof of \Cref{prop:gamma-factor-is-constant-on-lusztig-series} should be modified. We should first use $\GroupExtension{G}$. For this group we have the ``at most one cuspidal'' property. Then we should use \cite[Page 140]{DigneMichel2020} $$R_{\GroupExtension{T}}^{\GroupExtension{G}}\left(\tilde{\theta}\right) \restriction_{G} = R_{T}^G \left(\tilde{\theta}\restriction_{T}\right),$$
	where we need to explain the notation.
	\item Find what the root data + F action for the non-split quadratic form is. Find the dual gorup and add the appropriate representation to \Cref{lem:indep_geo_conj}
	\item We might be able to include $SO_{odd}$ with $\Phi(g)$ the symmetric function in the eigenvalues of $g$ given by $\sum_{i=1}^{dim(V)} \chi(\Pi_{j \neq i}(\lambda_j-1))$.

@@

\begin{theorem}\label{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}
	Suppose that $T \cong \prod_{j=1}^r \multiplicativegroup{\quadraticFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$ is a maximal torus of $H$. Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s$, where $\alpha_j \colon \multiplicativegroup{\quadraticFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$. Denote \begin{align*}
		g_T\left(\chi, \theta, \fieldCharacter\right)
		= & \prod_{i=1}^s \GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot \prod_{j=1}^r \GaussSumCharacter{\involution{\alpha_j}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}}.
	\end{align*} Then
	\begin{align*}
		 \dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \varepsilon_{\algebraicGroup{H}} R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) g_T\left(\chi, \theta, \fieldCharacter\right) \prod_{i=1}^s \theta_i\left(-1\right) \cdot \prod_{j=1}^r \alpha_j\left(-1\right).
	\end{align*}
\end{theorem}
\begin{proof}
	This follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{H}{T}}{\sizeof{H}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{H}_p^2 \cdot q^{\frac{\dim_{\finiteField} \hermitianSpace}{2}},$$
	and the fact \begin{equation*}
		\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^r.
	\end{equation*}
\end{proof}
\begin{remark}
	We have $$\varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}}.$$ If $\finiteField = \quadraticExtension$ then we also have $$\varepsilon_{\algebraicGroup{\GroupExtension{G}}} = \left(-1\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2} + 1}.$$
\end{remark}
\begin{remark}
	Suppose that $\pi$ is any irreducible representation of $H$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$. Then the central character of $\pi$ satisfies
	\begin{align*}
		\centralCharacter{\pi}\left(-1\right) = \theta\left(-1\right) =& \prod_{j=1}^r \alpha_j\left(-1\right) \cdot \prod_{i=1}^s \theta_i\left(-1\right).
	\end{align*}
	Thus \begin{align*}
		\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \centralCharacter{\pi}\left(-1\right) g_T\left(\chi, \theta, \fieldCharacter\right).
	\end{align*}
\end{remark}

@@

\begin{lemma}
\label{lem:cochar_computation}
    Define $\phi:(\mathbb{Q}/\mathbb{Z})_{p'}^n \to (\mathbb{Q}/\mathbb{Z})_{p'}^{2n} = X_*(\GL_{2n})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ by $\phi(x) = (x,-x)$. We will consider two different Frobeinus actions on these characters:
    \begin{enumerate}
        \item When $\Frobenius$ acts by trivially on both, $x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha})$
        \item When $\Frobenius$ acts by $-1$ on the domain and by $\begin{pmatrix}
            0 & 1 \\
            1 & 0\end{pmatrix}$ on the codomain, $x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$ where $\theta'(t) = \theta(t^{1-q^n})$
    \end{enumerate}
    \calvin{new cases:}
    \begin{enumerate}
        \item When $\Frobenius$ acts by an $n$-cycle $(12 \hdots n)$ on the preimage and the cycle $(12 \hdots n),(n+1,n+2 \hdots 2n)$ on the image, $x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha})$
        \item When $\Frobenius$ acts by $-1$ on the domain and by $\begin{pmatrix}
            0 & 1 \\
            1 & 0\end{pmatrix}$ on the codomain, $x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$ where $\theta'(t) = \theta(t^{1-q^n})$
        \item When 
    \end{enumerate}
\end{lemma}
\begin{proof}
Recall that $x_{T,\theta}$ is defined by for sufficiently large $m$ with $\zeta_m = 1/(q^m-1)$ under the fixed identification $\multiplicativegroup{\algebraicClosure{\finiteField}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}$
\[
    \exp(\langle x_{T,\theta},y\rangle) = \theta(y(N_{T(\finiteField_m):T(\finiteField)}(y(\zeta_m))).
\]
Thus the result follows from the computations:
\begin{enumerate}
	\item \begin{align*}
		\exp(\langle\phi(x_{\finiteFieldExtension{n},\alpha}),(y_1,y_2)\rangle) &= \exp(\langle x_{\finiteFieldExtension{n},\alpha},\phi^*(y_1,y_2)\rangle) \\
		&= \alpha\left(\FieldNorm{mn}{n}(y_1(\zeta_{mn})\right) \alpha\left(\FieldNorm{mn}{n}(y_2(\zeta_{mn})\right)^{-1} \\
		&= \left(\alpha\times\alpha^{-1}\right)\left(\FieldNorm{mn}{n}((y_1,y_2)(\zeta_{mn}))\right)
	\end{align*}
	\item \begin{align*}
		\exp(\langle\phi(x_{\NormOneGroup{2n},\theta}),(y_1,y_2)\rangle) &= \exp(\langle x_{\NormOneGroup{2n},\theta},\phi^*(y_1,y_2)\rangle) \\
		&= \theta\left(\frac{\FieldNorm{2mn}{2n}(y_1(\zeta_{2mn})}{\FieldNorm{2mn}{2n}\left(y_1(\zeta_{2mn})^{q^n}\right)}\right) \theta\left(\frac{\FieldNorm{2mn}{2n}(y_2(\zeta_{2mn})}{\FieldNorm{2mn}{2n}\left(y_2(\zeta_{2mn})^{q^n}\right)}\right)^{-1} \\
		&= \theta'\left(\FieldNorm{2mn}{2n}((y_1,y_2)(\zeta_{mn}))\right)
	\end{align*}
\end{enumerate}
\end{proof}

@@

\calvin{end alternate writeup}
\end{comment}
\calvin{start alternate writeup 2 of section 3.4/3.4.1}
\subsection{Computation for Lusztig Series}
The goal of this section is to prove \Cref{thm:Phi_stable} in particular:
\begin{theorem}
\label{thm:doubling-method-gamma-factor-for-deligne-lusztig} For either $G=G$ or its group extension $\GroupExtension{G}$. If $c_{\pi}$ is nonzero in the virtual representation $R_T(\theta) = \sum c_{\pi} \pi$ then
$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$
\end{theorem}
\calvin{add in $\chi$} the right hand side of which we showed in \Cref{lem:indep_geo_conj} only depends on the geometric conjugacy class of $(T,\theta)$ hence on the Lusztig series $\LusztigSeries{G}{s}$ which contains $\pi$.
\subsubsection{Proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}, \Cref{thm:Phi_stable}}
We first reduce \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} to the case $G$ has connected center. For any irreducible representation $\pi$ of $G$ which is the a component of an irreducible representation $\tilde{\pi}$ of $\GroupExtension{G}$ restricted to $\pi$,
\[
    \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\tilde{\pi}}{\chi}{\fieldCharacter}.
\]

@@

By \Cref{lem:indep_geo_conj}, we know that for $R_T(\theta) = \sum c_{\pi} \pi$, 
$$\sum c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = (\sum c_{\pi})g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$.
Since we know the relevant equality for non cupsidal $\pi$, we get that
$$ \sum_{\pi \textnormal{ cuspidal}} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \left(\sum_{\pi \textnormal{ cuspidal}} c_{\pi}\right)g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$.

But it is well known that there is only one cuspidal $\pi$ appearing in our sum:
\begin{proposition}[{\cite[Page 172]{Lusztig1977}}]
	Let $\GroupExtension{G}$ have connected center. For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ contains at most one cuspidal element.
\end{proposition}

>>>>

\subsection{TODO list}
\begin{enumerate}
	\item In the computations of $\dblGammaFactor{\pi}{\chi}{\fieldCharacter}$ in terms of Deligne--Lusztig we should say that when we take a torus of $\GroupExtension{G}$ and intersect it with $G$ we get a torus of $G$ and hence it suffices to compute whatever we are computing.
	\item The proof of \Cref{prop:gamma-factor-is-constant-on-lusztig-series} should be modified. We should first use $\GroupExtension{G}$. For this group we have the ``at most one cuspidal'' property. Then we should use \cite[Page 140]{DigneMichel2020} $$R_{\GroupExtension{T}}^{\GroupExtension{G}}\left(\tilde{\theta}\right) \restriction_{G} = R_{T}^G \left(\tilde{\theta}\restriction_{T}\right),$$
	where we need to explain the notation.
	\item Find what the root data + F action for the non-split quadratic form is. Find the dual gorup and add the appropriate representation to \Cref{lem:indep_geo_conj}

@@

\begin{theorem}\label{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}
	Suppose that $T \cong \prod_{j=1}^r \multiplicativegroup{\quadraticFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$ is a maximal torus of $H$. Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s$, where $\alpha_j \colon \multiplicativegroup{\quadraticFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$. Denote \begin{align*}
		g_T\left(\chi, \theta, \fieldCharacter\right)
		= & \prod_{i=1}^s \GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot \prod_{j=1}^r \GaussSumCharacter{\involution{\alpha_j}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}}.
	\end{align*} Then
	\begin{align*}
		 \dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \varepsilon_{\algebraicGroup{H}} R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) g_T\left(\chi, \theta, \fieldCharacter\right) \prod_{i=1}^s \theta_i\left(\pm 1\right) \cdot \prod_{j=1}^r \alpha_j\left(\pm 1\right).
	\end{align*}
	\elad{Modify this so it is also true in the odd special orthogonal group case: it is zero for $-$ and there are factors $\theta\left(2\right)$ for $+$}
\end{theorem}
\begin{proof}
	This follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{H}{T}}{\sizeof{H}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{H}_p^2 \cdot q^{\frac{\dim_{\finiteField} \hermitianSpace}{2}},$$
	and the fact \begin{equation*}
		\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^r.
	\end{equation*}
\end{proof}
\begin{remark}
	We have $$\varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}}.$$ If $\finiteField = \quadraticExtension$ then we also have $$\varepsilon_{\algebraicGroup{\GroupExtension{G}}} = \left(-1\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2} + 1}.$$
\end{remark}
\begin{remark}
	Suppose that $\pi$ is any irreducible representation of $H$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$. Then the central character of $\pi$ satisfies
	\begin{align*}
		\centralCharacter{\pi}\left(-1\right) = \theta\left(-1\right) =& \prod_{j=1}^r \alpha_j\left(-1\right) \cdot \prod_{i=1}^s \theta_i\left(-1\right).
	\end{align*}
	Thus \begin{align*}
		\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \centralCharacter{\pi}\left(-1\right) g_T\left(\chi, \theta, \fieldCharacter\right).
	\end{align*}
\end{remark}

@@

\begin{lemma}
\label{lem:cochar_computation}
    Define $\phi:(\mathbb{Q}/\mathbb{Z})_{p'}^n \to (\mathbb{Q}/\mathbb{Z})_{p'}^{2n} = X_*(\GL_{2n})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ by $\phi(x) = (x,-x)$. We will consider two different Frobeinus actions on these characters:
        \item When $\Frobenius$ acts by trivially on both, $x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha})$
        \item When $\Frobenius$ acts by $-1$ on the domain and by $\begin{pmatrix}
            0 & 1 \\
            1 & 0\end{pmatrix}$ on the codomain, $x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$ where $\theta'(t) = \theta(t^{1-q^n})$
    \calvin{new cases:}
    Let $\phi:X_*(\algebraicGroup{T}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^n \to X_*(\tilde{\algebraicGroup{T}}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^{2n}$ send $x$ to $(x,-x)$. Then we have the following cases corresponding to conjugacy classes in the Weyl group
        \item[B,C,D Case 1)] $w$ is conjugate to an $n$-cycle: \calvin{Add in note about the two type B cases} In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $w$ on the preimage and the cycle $(w,w)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha})$$
        \item[B,C,D Case 2)] $w$ is conjugate to an $n$-cycle with one negative:
 In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{U}(1)$ with $\Frobenius$ acting by $w$ on the preimage and by a $2n$ cycle on the image, and $$x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n})$
    \item[$G=\algebraicGroup{U}$ Case 1)] $w$ is conjugate to $(1,2 \hdots n)$ an even cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the product of two $n$ cycles $\begin{pmatrix} w & 0 \\
        0 & w
        \end{pmatrix} \cdot \begin{pmatrix} 0 & I\\I & 0
        \end{pmatrix}$  on the image, and 
        \item[$G=\algebraicGroup{U}$ Case 2)] $w$ is conjugate to $(1,2 \hdots n)$ an odd cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{U}(1)$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the $2n$ cycle $\begin{pmatrix} w & 0 \\
        0 & w
        \end{pmatrix} \cdot \begin{pmatrix} 0 & I\\I & 0
        \end{pmatrix}$ on the image , and $$x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n})$
\end{lemma}
\begin{proof}
Recall that $x_{T,\theta}$ is defined by for sufficiently large $m$ with $\zeta_m = 1/(q^m-1)$ under the fixed identification $\multiplicativegroup{\algebraicClosure{\finiteField}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}$
\[
    \exp(\langle x_{T,\theta},y\rangle) = \theta(y(N_{T(\finiteField_m):T(\finiteField)}(y(\zeta_m))).
\]
Thus the result follows from the computations:
	\item \begin{align*}
		\exp(\langle\phi(x_{\finiteFieldExtension{n},\alpha}),(y_1,y_2)\rangle) &= \exp(\langle x_{\finiteFieldExtension{n},\alpha},\phi^*(y_1,y_2)\rangle) \\
		&= \alpha\left(\FieldNorm{mn}{n}(y_1(\zeta_{mn})\right) \alpha\left(\FieldNorm{mn}{n}(y_2(\zeta_{mn})\right)^{-1} \\
		&= \left(\alpha\times\alpha^{-1}\right)\left(\FieldNorm{mn}{n}((y_1,y_2)(\zeta_{mn}))\right)
	\end{align*}
	\item \begin{align*}
		\exp(\langle\phi(x_{\NormOneGroup{2n},\theta}),(y_1,y_2)\rangle) &= \exp(\langle x_{\NormOneGroup{2n},\theta},\phi^*(y_1,y_2)\rangle) \\
		&= \theta\left(\frac{\FieldNorm{2mn}{2n}(y_1(\zeta_{2mn})}{\FieldNorm{2mn}{2n}\left(y_1(\zeta_{2mn})^{q^n}\right)}\right) \theta\left(\frac{\FieldNorm{2mn}{2n}(y_2(\zeta_{2mn})}{\FieldNorm{2mn}{2n}\left(y_2(\zeta_{2mn})^{q^n}\right)}\right)^{-1} \\
		&= \theta'\left(\FieldNorm{2mn}{2n}((y_1,y_2)(\zeta_{mn}))\right)
	\end{align*}
\end{proof}

@@

\calvin{end alternate writeup}
\end{comment}
\calvin{start alternate writeup 2 of section 3.4/3.4.1}
\subsection{Computation for Lusztig Series}
The goal of this section is to prove \Cref{thm:Phi_stable} in particular:
\begin{theorem}
\label{thm:doubling-method-gamma-factor-for-deligne-lusztig} For either $G=G$ or its extension $\GroupExtension{G}$. If $c_{\pi}$ is nonzero in the virtual representation $R_T(\theta) = \sum c_{\pi} \pi$ then
$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$
\end{theorem}
\calvin{add in $\chi$} the right hand side of which we showed in \Cref{lem:indep_geo_conj} only depends on the geometric conjugacy class of $(T,\theta)$ hence on the Lusztig series $\LusztigSeries{G}{s}$ which contains $\pi$, implying \Cref{thm:Phi_stable}.
\subsubsection{Proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}}
We first reduce \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} to the case $G$ has connected center. For any irreducible representation $\pi$ of $G$ which is the a component of an irreducible representation $\tilde{\pi}$ of $\GroupExtension{G}$ restricted to $\pi$,
\[
    \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\tilde{\pi}}{\chi}{\fieldCharacter}.
\]

@@

Combining this with our inductive hypothesis implies \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for non cupsidal $\pi$.
By \Cref{lem:indep_geo_conj}, we know that for $R_T(\theta) = \sum c_{\pi} \pi$, 
$$\sum c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = (\sum c_{\pi})g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$. Subtracting our the equality for non-cupsidal $\pi$ we are left with:
$$ \sum_{\pi \textnormal{ cuspidal}} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \left(\sum_{\pi \textnormal{ cuspidal}} c_{\pi}\right)g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$.

But it is well known that there is only one cuspidal $\pi$ appearing in our sum:
\begin{proposition}[{\cite[Page 172]{Lusztig1977}}]
	Let $\GroupExtension{G}$ be a classical group with connected center. For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ contains at most one cuspidal element.
\end{proposition}
